Formal Analysis of Rate-Monotonic Scheduling Implementation via Real-Time Maude

### 2015-10-02 RMS/submission.tex
writing section verification

\section{Formal Analysis}
\subsection{Properties}
\subsection{Completeness of the Analysis}

>>>>

\section{Formal Verification}
Although Real-Time Maude provides many useful commands and tools to
analyze a model, such as, \verb|rewrite| to execute the model,
\verb|search| to search some reachable state(s) satisfying given
properties from the initial state, the Maude Inductive Theorem Prover
(ITP) to interactively prove properties written in \emph{membership
  equational logic}, and so on, we concentrate in this paper on using
the model checking tool to verify the desired properties of our model.

In this section, we analyze our model of the RMS implementation under
several different scenarios, containing both realistic and
experimental ones.

The main objective is to verify the schedubility of a given set of
periodic tasks. Therefore we define an atomic proposition
\verb|taskTimeout| to hold if there exists an \verb|error| appearing
in the $taskList$ of the current state:
\begin{verbatim}
  op taskTimeout : -> Prop [ctor] .
  eq {L T STS HW ISRC} |= taskTimeout = containError(L) .
\end{verbatim}

\subsection{Properties Formalism}

\subsection{Completeness of the Analysis}
